Efficient Coalition Formation \\ for Web Services

### 2013-06-06 papers/coalition-journal-extension/coalition_journal.tex
Changes

We present an example with a community with $R_C$ value of 10, and three web services each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}.

>>>>

We present an example with a community with $R_C$ value of 10, and three web services each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}. The worth of a community is calculated based on $Out(C)$ equation (\ref{xxxxxx}) which is amount of output being generated by the community. Web services working individually, without joining a community, have small market shares. The first table shows in figure \ref{xxxxxx} lists the web services with their aggregated $QoS_{ws}$ parameters, their task input rate while working alone, and also their $Th_{ws}$ throughput value. The second table shows all the possible communities and their worth. The values suggest, communities having more web services have better gain and output. However community tries to distribute the gain between web services. Sometimes it is impossible to share the gain between all web services in a way no subset of them would individually gain more if they had their own group. In our example, as listed at table \ref{xxxxxx}, web services {ws_1} and {ws_2} working together can gain
